### 2012-05-02 inst/examples/policycosts/stochastic_norms.Rmd
fixed third profit plot
updated fixed costs

## @knitr profit_
profit <- profit_harvest(price = 10, c0 = 30, c1 = 10)

@@

``` {r fees}
L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
fixed <-  function(c2) function(h, h_prev) c2
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
````

@@

``` {r policycost_optim}
c2 <- 4
penalty <- fixed(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

@@

qplot(costs$V1)
qplot(profits$V1)
qplot(profits-costs$V1)
````

>>>>

## @knitr profit_
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)

@@

``` {r fees}
L1 <- function(c2) function(h, h_prev)  c2 * abs(h - h_prev) 
free_increase <- function(c2) function(h, h_prev)  c2 * abs(min(h - h_prev, 0)) # increasing harvest is free
free_decrease <- function(c2) function(h, h_prev)  c2 * max(h - h_prev, 0) # decreasing harvest is free
fixed <-  function(c2) function(h, h_prev) c2 * as.numeric( !(h == h_prev) )
L2 <- function(c2) function(h, h_prev)  c2 * (h - h_prev) ^ 2
````

@@

``` {r policycost_optim }
c2 <- 4.0
penalty <- fixed(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

@@

qplot(costs$V1)
qplot(profits$V1)
qplot(profits$V1-costs$V1)
````
